26 Years of Water Quality Change in Rhode Island Lakes and Ponds

### 2019-01-30 manuscript/manuscript.Rmd
few updates

During the sampling period of 1990 to 2016 Rhode Island lakes and ponds average lake temperature was `r paste(ww_param_ranges%>%filter(Parameter == "temp")%>%pull(Mean), ww_param_ranges%>%filter(Parameter == "temp")%>%pull(Units))`, average total nitrogen was `r paste(ww_param_ranges%>%filter(Parameter == "total_n")%>%pull(Mean), ww_param_ranges%>%filter(Parameter == "total_n")%>%pull(Units))`, average total phosphorus was `r paste(ww_param_ranges%>%filter(Parameter == "total_p")%>%pull(Mean), ww_param_ranges%>%filter(Parameter == "total_p")%>%pull(Units))`, and average chlorophyll was `r paste(ww_param_ranges%>%filter(Parameter == "chla")%>%pull(Mean), ww_param_ranges%>%filter(Parameter == "chla")%>%pull(Units))` (`r tab_num("ww_params", display = "cite", caption = "Summary statistics for URI Watershed Watch data from 1990 to 2016.")`).  For lakes in ponds in the larger region represented by the LAGOSNE States,  average total nitrogen was `r paste(lagos_param_ranges%>%filter(Parameter == "total_n")%>%pull(Mean), lagos_param_ranges%>%filter(Parameter == "total_n")%>%pull(Units))`, average total phosphorus was `r paste(lagos_param_ranges%>%filter(Parameter == "total_p")%>%pull(Mean), lagos_param_ranges%>%filter(Parameter == "total_p")%>%pull(Units))`, and average chlorophyll was `r paste(lagos_param_ranges%>%filter(Parameter == "chla")%>%pull(Mean), lagos_param_ranges%>%filter(Parameter == "chla")%>%pull(Units))` (`r tab_num("lagos_params", display = "cite", caption = "Summary statistics for URI Watershed Watch data from 1990 to 2016.")`).

@@

@@

*`r fig_num(name = "tp_ri", caption = "Yearly trend over 20+ years of Total Phosphorus (average z-score) in Rhode Island lakes and ponds.")`*

@@

*`r fig_num(name = "chla_ri", caption = "Yearly trend over 20+ years of Chlorphyll *a* (average z-score) in Rhode Island lakes and ponds.")`*

@@

*`r fig_num(name = "tn_lagos", caption = "Yearly trend over 20+ years of Total Nitrogen (average z-score) in the LAGOSNE states.")`*

@@

*`r fig_num(name = "tp_lagos", caption = "Yearly trend over 20+ years of Total Phosphorus (average z-score) in the LAGOSNE states.")`*

@@

*`r fig_num(name = "chla_lagos", caption = "Yearly trend over 20+ years of Chlorophyll *a* (average z-score) in the LAGOSNE states.")`*

>>>>

During the sampling period of 1990 to 2016 Rhode Island lakes and ponds average lake temperature was `r paste(ww_param_ranges%>%filter(Parameter == "temp")%>%pull(Mean), ww_param_ranges%>%filter(Parameter == "temp")%>%pull(Units))`, average total nitrogen was `r paste(ww_param_ranges%>%filter(Parameter == "total_n")%>%pull(Mean), ww_param_ranges%>%filter(Parameter == "total_n")%>%pull(Units))`, average total phosphorus was `r paste(ww_param_ranges%>%filter(Parameter == "total_p")%>%pull(Mean), ww_param_ranges%>%filter(Parameter == "total_p")%>%pull(Units))`, and average chlorophyll was `r paste(ww_param_ranges%>%filter(Parameter == "chla")%>%pull(Mean), ww_param_ranges%>%filter(Parameter == "chla")%>%pull(Units))` (`r tab_num("ww_params", display = "cite", caption = "Summary statistics for URI Watershed Watch data from 1990 to 2016.")`).

@@

For lakes in ponds in the larger region represented by the LAGOSNE States,  average total nitrogen was `r paste(lagos_param_ranges%>%filter(Parameter == "total_n")%>%pull(Mean), lagos_param_ranges%>%filter(Parameter == "total_n")%>%pull(Units))`, average total phosphorus was `r paste(lagos_param_ranges%>%filter(Parameter == "total_p")%>%pull(Mean), lagos_param_ranges%>%filter(Parameter == "total_p")%>%pull(Units))`, and average chlorophyll was `r paste(lagos_param_ranges%>%filter(Parameter == "chla")%>%pull(Mean), lagos_param_ranges%>%filter(Parameter == "chla")%>%pull(Units))` (`r tab_num("lagos_params", display = "cite", caption = "Summary statistics for URI Watershed Watch data from 1990 to 2016.")`).

@@

(`r fig_num(name = "tp_ri", caption = "Yearly trend over 20+ years of Total Phosphorus (average z-score) in Rhode Island lakes and ponds.", display = "cite")`).

*`r fig_num(name = "tp_ri")`*

@@

(`r fig_num(name = "chla_ri", caption = "Yearly trend over 20+ years of Chlorphyll a (average z-score) in Rhode Island lakes and ponds.", display = "cite")`).

*`r fig_num(name = "chla_ri")`*

@@

(`r fig_num(name = "tn_lagos", caption = "Yearly trend over 20+ years of Total Nitrogen (average z-score) in the LAGOSNE states.", display = "cite")`).

*`r fig_num(name = "tn_lagos")`*

@@

(`r fig_num(name = "tp_lagos", caption = "Yearly trend over 20+ years of Total Phosphorus (average z-score) in the LAGOSNE states.",display = "cite")`).

*`r fig_num(name = "tp_lagos")`*

@@

(`r fig_num(name = "chla_lagos", caption = "Yearly trend over 20+ years of Chlorophyll a (average z-score) in the LAGOSNE states.", display = "cite")`).

*`r fig_num(name = "chla_lagos")`*
